Delta Smelt Enclosure Study 2019 Hybrid Paper Diet Analysis

### 2023-06-09 smelt_2019_allseasons/Diet 2019.Rmd
catching up on my git hub
exporting final dataframe to data_clean folder

#remove new date column
weird.tag <- subset(weird.tag, select = -6)

@@

library(scales)
show_col(viridis_pal(option = "plasma")(8))
viridis_pal(option = "plasma")(8)
```

>>>>

#remove new date column
weird.tag <- select(weird.tag, -X.date)

@@

library(scales)
show_col(viridis_pal(option = "plasma")(8))
viridis_pal(option = "plasma")(8)

write.csv(prop2, "smelt_2019_allseasons/data_clean/Diet.proportions.csv", row.names=FALSE)
```
